%Note: any items denoted by xxxx ... xxxx are ``fix-me'' items.

\documentclass[12pt,letterpaper]{report}
\usepackage{natbib}
\usepackage{geometry}
%\usepackage{fancyheadings} fancyheadings is obsolete: replaced by fancyhdr. JL
\usepackage{fancyhdr}
\usepackage{afterpage}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsbsy}
\usepackage{dcolumn,array}
\usepackage{tocloft}
\usepackage{asudis}

%-----------------------Packages I use. JL
\usepackage{caption}

%-----------------------Commands I use. JL
\newcommand{\pd}{\partial} % shorter.
\newcommand{\pr}{\prime} % shorter.
\newcommand{\ket}[1]{\left| #1 \rangle\right.} % for Dirac kets 
\newcommand{\bra}[1]{\langle #1 |} % for Dirac bras
\newcommand{\braket}[2]{\langle #1 \vphantom{#2} |
  #2 \vphantom{#1} \rangle} % for Dirac brackets
\newcommand{\ketbra}[2]{| #1 \vphantom{#2} \rangle 
  \!\ \!\langle #2 \vphantom{#1} |} % for Dirac ketbras
\newcommand{\matrixel}[3]{\langle #1 \vphantom{#2#3} |
 #2 | #3 \vphantom{#1#2} \rangle} % for Dirac matrix elements
% for momentum integrals
\newcommand{\pint}[2]{\int\!\!\frac{d^{#1}#2}{(2\pi)^{#1}}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\gvec}[1]{\boldsymbol{#1}}
\newcommand{\up}{\uparrow}
\newcommand{\down}{\downarrow}

\defcitealias{national2012nuclear}{The NP2010 Committee, 2012}

\begin{document}
%-----------------------front matter
\pagenumbering{roman}
\title{Quantum Monte Carlo Calculations of Light Nuclei with Non-Local 
Potentials}
\author{Joel E. Lynn}
\degreeName{Doctor of Philosophy}
\defensemonth{April}
\gradmonth{May}
\gradyear{2013}
\chair{Kevin Schmidt}
\memberOne{Ricardo Alarc\'on}
\memberTwo{Richard Lebed}
\memberThree{Igor Shovkovy}
\memberFour{John Shumway}

\maketitle
\doublespace
\include{abstract}
\dedicationpage{I dedicate this thesis to my family, who are the foundation
upon which everything else is built. 
\linebreak
\linebreak
To my wife and best 
friend, Jessica: You have always been and always will be my partner in all 
things.  Without your
love, support, and infinite patience none of this would have happened: I 
would not be who I am today without you.  We are two birds getting lost upon 
their way.  
\linebreak
\linebreak
To my son, Isaac: You are a continuing
source of inspiration.  You ask me tough questions, like ``what did the 
universe look like before the big bang?''  Seeing your curiosity about our world
sharpens my own.
\linebreak
\linebreak
To my son, Owen: Your energy and spirit are rejuvenating.  At the end of a day
when nothing else may have worked or made sense, coming home and hearing you
call my name as you ran to the door set everything right.
\linebreak
\linebreak
To my daughter, Kelsey: Your smile and laughter brightened many cloudy days.
You are my Telsey-bird, Telsey-bird oh so sweet!  
}
\include{ack}
\tableofcontents
\addtocontents{toc}{~\hfill Page\par}
\newpage
\addcontentsline{toc}{part}{LIST OF TABLES}
\renewcommand{\cftlabel}{Table}
\listoftables
\addtocontents{lot}{Table~\hfill Page \par}
\newpage
\addcontentsline{toc}{part}{LIST OF FIGURES}
\addtocontents{toc}{CHAPTER \par}
\renewcommand{\cftlabel}{Figure}
\listoffigures
\addtocontents{lof}{Figure~\hfill Page \par}
%-----------------------body
\doublespace
\pagenumbering{arabic}
\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}
\include{chapter6}
%-----------------------back matter
{\singlespace
\addcontentsline{toc}{part}{REFERENCES}
\bibliographystyle{asudis}
\bibliography{dis}}
%\labeltoc{Appendix}
\renewcommand{\chaptername}{APPENDIX}
\addtocontents{toc}{APPENDIX \par}
\appendix
\include{appendix1}
\include{vita}
\end{document}
